\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2021-02-10 sections/methods.tex
Update manuscript to address comment R2.1.2
Fix minor typos and sentence structure improvement

  \subsection*{Network Inference (NI)}
  \vspace{-5mm}
  This module deals with the inference of co-occurrence associations from the \ac{otu} or \ac{esv} counts matrix.
  These associations can be represented as a network, with nodes representing taxonomies of the micro-organisms and edges representing the association between them.
  A null model is created by re-sampling and bootstrapping the correlation/interaction matrix and is used to calculate the significance of the inferred associations by calculating the p-values against this null model \cite{Watts2018}.
  The pipeline includes Pearson, Spearman and FastSpar v0.0.10 (a faster implementation of \ac{sparcc})~\cite{Watts2018} as the pairwise correlation metrics, and \ac{spieceasi} v1.0.7~\cite{Kurtz2015}, \ac{mldm} v1.1~\cite{Yang2017} and \ac{magma}~\cite{Cougoul2019} as the direct association metrics.
  The Brown's p-value merging method~\cite{brown_400_1975} is used for combining p-values from the various methods to obtain a consensus p-value, which is used to create the consensus network.

>>>>

  \subsection*{Network Inference (NI)}
  \vspace{-5mm}
  This module deals with the inference of co-occurrence associations from the \ac{otu} or \ac{esv} counts matrix.
  The counts matrices are collapsed to the Genus level (or the required taxonomy level) by adding up the counts of \ac{otu} or \ac{esv} that map to the same taxa.
  These collapsed matrices are as used as input to the network inferrence methods to produce association matrices at the appropriate taxonomy level.
  These associations can be represented as a network, with nodes representing taxonomies of the micro-organisms and edges representing the associations between them.
  A null model is created by re-sampling and bootstrapping the correlation/interaction matrix and is used to calculate the significance of the inferred associations by calculating the p-values against this null model~\cite{Watts2018}.
  The pipeline includes Pearson, Spearman and FastSpar v0.0.10 (a faster implementation of \ac{sparcc})~\cite{Watts2018} as the pairwise correlation metrics, and \ac{spieceasi} v1.0.7~\cite{Kurtz2015}, \ac{mldm} v1.1~\cite{Yang2017} and \ac{magma}~\cite{Cougoul2019} as the direct association metrics.
  The Brown's p-value merging method~\cite{brown_400_1975} is used for combining p-values from the various methods to obtain a consensus p-value, which is used to create the consensus network.

### 2021-02-10 sections/results.tex
Fix minor typos and sentence structure improvement

  The representative sequences obtained from the \ac{dada2} method in DC step were used for taxonomic assignment using the three reference databases.
  Figure~\ref{fig:figure4}A depicts a flow diagram that shows how the top 50 representative sequences (sorted by abundance) are assigned a Genus according to the three different databases.
  We observe that not only does the assigned Genus composition vary significantly, but the percentage of unassigned representative sequences (gray) also differ.
  Even the most abundant representative sequence is assigned to an "unknown" Genus in two of the three databases.
  A representative sequence might be assigned an "unknown" Genus for one of two reasons: the first is if the taxonomy identifier associated with the sequence in the database did not contain a Genus; the second (more likely) reason is that the database contains multiple sequences that are very similar to the query (representative) sequence and the consensus algorithm (from \ac{qiime2}) is unable to assign one particular Genus at the required confidence.
  After assigning all the representative sequences to taxonomies we perform a pairwise comparison of the similarity between assignments from different databases at every taxonomic level (Figure~\ref{fig:figure4}B).
  The assignments beyond Family level (Family, Genus and Species) are very dissimilar with $<70\%$ similarity between any pair of databases.
  There are no two reference databases that are more similar than the other pairs, with \ac{gg} and SILVA producing only marginally similar assignments compared to \ac{ncbi}.
  This implies that the taxonomy assignments from each reference database are fairly unique and are largely responsible for the differences observed in the co-occurrence networks generated from different taxonomy databases.

@@

  Given that no database performs better than others against mock datasets, and that databases are almost equally distant from each other in terms of final output, the choice of which database to use should be driven by other reason.
  One user-specific way to choose, would be based on the known representation of taxa for the microbiome of interest (see also Discussion). Another reason could be the frequency of updates and the potential for future growth, which prompted us to set \ac{ncbi} as the \ac{micone} standard for taxonomy assignment.
 In addition to being regularly maintained and updated the \ac{ncbi} database already has the advantage that its accuracy of assignments is still comparable to the SILVA and \ac{gg} reference databases that are routinely used as reference databases.

>>>>

  The representative sequences obtained from the \ac{dada2} method in the DC step were used for taxonomic assignment using the three reference databases.
  Figure~\ref{fig:figure4}A depicts a flow diagram that shows how the top 50 representative sequences (sorted by abundance) are assigned a Genus according to the three different databases.
  % TOOD: Update with a more quantitative description
  We observe that not only does the assigned Genus composition vary significantly, but the percentage of unassigned representative sequences (gray) also differ.
  Even the most abundant representative sequence is assigned to an "unknown" Genus in two of the three databases.
  A representative sequence might be assigned an "unknown" Genus for one of two reasons: the first is if the taxonomy identifier associated with the sequence in the database did not contain a Genus; the second (more likely) reason is that the database contains multiple sequences that are very similar to the query (representative) sequence and the consensus algorithm (from \ac{qiime2}) is unable to assign one particular Genus at the required confidence.
  After assigning all the representative sequences to taxonomies we perform a pairwise comparison of the similarity between assignments from different databases at every taxonomic level (Figure~\ref{fig:figure4}B).
  The assignments beyond Family level (Family, Genus and Species) are very dissimilar with $<70\%$ similarity between any pair of databases.
  There are no two reference databases that are more similar than the other pairs, with \ac{gg} and SILVA producing only marginally similar assignments compared to \ac{ncbi}.
  This implies that the taxonomy assignments from each reference database are fairly unique and are largely responsible for the differences observed in the co-occurrence networks generated from different taxonomy databases.

@@

  Given that no database performs better than others against mock datasets, and that databases are almost equally distant from each other in terms of final output, the choice of which database to use should be driven by other reasons.
  One user-specific way to choose, would be based on the known representation of taxa for the microbiome of interest (see also Discussion). Another reason could be the frequency of updates and the potential for future growth, which prompted us to set \ac{ncbi} as the \ac{micone} standard for taxonomy assignment.
 In addition to being regularly maintained and updated the \ac{ncbi} database already has the advantage that its accuracy of assignments is still comparable to the SILVA and \ac{gg} reference databases that are routinely used as reference databases.

### 2021-02-10 sections/tables_figures.tex
Update manuscript to address comment R2.5
Fix minor typos and sentence structure improvement

  \begin{figure}[H]
    \centering
    \includegraphics[width=0.85\linewidth]{figure2.pdf}
  \end{figure}
  \begin{figure}[H]
    \centering
      \caption{
      \textbf{The choice of database contributes to the most variance in the networks}.
      \textbf{(A)} The total relative variance in the networks contributed by the DC, TA and OP steps of the pipeline (right) and the linear model used to calculate the relative variance (left), see the Methods section for details.
      \textbf{(B)} All combinations of inferred networks are shown as points on a PCA plot.
      The color of the points corresponds to the taxonomy database, the shape corresponds to the denoising/clustering method and the size corresponds to whether low abundance OTUs were removed or not.
      \textbf{(B inset)} The network generated using DC=dada2, TA=GG, OP=no and NI=SPARCC and represents the particular point shown (big red square).
      The plot clearly shows that the points can be separated based on the TA step and that the differences due to the DC and OP steps are not as significant.
    }
    \label{fig:figure2}
  \end{figure}
  \FloatBarrier
  \newpage

>>>>

  \begin{figure}[H]
    \centering
    \includegraphics[width=0.85\linewidth]{figure2.pdf}
  \end{figure}
  \begin{figure}[H]
    \centering
      \caption{
      \textbf{The choice of database contributes to the most variance in the networks}.
      \textbf{(A)} The total relative variance in the networks contributed by the DC, TA and OP steps of the pipeline (right) and the linear model used to calculate the relative variance (left), see the Methods section for details.
      \textbf{(B)} All combinations of inferred networks are shown as points on a PCA plot.
      The color of the points corresponds to the taxonomy database, the shape corresponds to the denoising/clustering method and the size corresponds to whether low abundance OTUs were removed or not.
      \textbf{(B inset)} The network generated using DC=dada2, TA=GG, OP=no and NI=SPARCC and represents the particular point shown (big red square).
      The points on the PCA plot can be separated based on the TA step and the differences due to the DC and OP steps are comparatively not as significant.
    }
    \label{fig:figure2}
  \end{figure}
  \FloatBarrier
  \newpage
